---
title: 'HW 1: Create an RMarkdown Report'
author: "Jiacheng Zhou"
date: "2019/6/3"
output: 
    html_document:
        toc: true
        theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Introduction
The project I would like to introduce is a research I did last semester in a class called "Urban Informatics". The name of the project is "DATAMINING THE TAXI: Explorative Analysis on Yellow Taxi Trips Based on Zoning Features in Brooklyn". Here is the link of [my project](https://trailblazercj03.github.io/Urban_Info_Final/). Python is used to visualize the taxi trajectory.

This html file has been published to the Rpubs and here's the [link](http://rpubs.com/CJ_McCollum03/QMSS_HW1).

# Context
## Study Area
The study area of the project is borough Brooklyn, New York, and the spatial unit that is used is "zoning features".

## Research Aim
1. To understand the usage and characteristics of the yellow taxi in the borough of Brooklyn in October 2015.
2. To understand the relationships between people's behaviors of taking yellow cabs and different zoning features, including Residential Districts(R), Commercial Districts (C), Manufacturing Districts (M), Park Areas (P).
3. To visualize the typical trips and identify the populous/typical trips in Brooklyn.

##Mapping
Other mapping skills are used such as heat map to show the difference of taxi trips between weekdays and weekends.

# Including Plots

You can also embed plots, for example:

```{r mpg, echo=TRUE}
m=mtcars
plot(mtcars$mpg)
```

